Effect of Election on Currency Fluctuation

### 2024-04-09 paper/paper.qmd
tested alternative model designs, abandoned new approaches and sticking to the initial version. Updated paper title, added TOC and created a plot illustrating data size difference between treatment and control

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

>>>>

---
title: "Effect of Election on Currency Fluctuation"
subtitle: "Analysis of USD Exchange Rate Fluctuation during Inaugurtion week"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/election-season-and-currency-fluctuation.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(readr)
library(rstanarm)
library(knitr)
library(modelsummary)
library(ggplot2)
```

@@

```{r}
exchange_inaug |>
  ggplot(aes(
    x = date,
    y = exchange_rate
  )) +
  geom_point(alpha = 0.005) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 0),
    method = "lm",
    color = "grey",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1974-08-06" & date <= "1974-08-12"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1977-01-17" & date <= "1977-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1981-01-17" & date <= "1981-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1989-01-17" & date <= "1989-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "1993-01-17" & date <= "1993-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2001-01-17" & date <= "2001-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2009-01-17" & date <= "2009-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2017-01-17" & date <= "2017-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  ) +
  geom_smooth(
    data = exchange_inaug |> filter(inauguration_period == 1 & date >= "2021-01-17" & date <= "2021-01-23"),
    method = "lm",
    color = "blue",
    formula = "y ~ x"
  )

```
